\mytitile\\~

### 2020-01-19 document.tex
add minor corrections
Updates

	\includegraphics[width=.495\linewidth]{main_picture_slices}
	\includegraphics[width=.495\linewidth]{stationary}
	\caption{Two-tone spectroscopy: experiment 
	and numerical modelling. \textbf{(a)} 
	Experimental data. Colour shows the real part 
	of complex transmission  through the sample. 
	Two transmons are aligned as in 
	\autoref{fig:experiment}~(c) and form a 
	symmetric picture. Experimental data contain 
	an additional horizontal line from a 
	parasitic resonance interacting with the 
	readout resonator. Three avoided crossings 
	not predicted by the unperturbed model are 
	shown in insets I, II and III; other 
	pronounced features reproduced by the 
	modelling are shown with Arabic markers (see 
	text for description). \textbf{(b)} Numerical 
	simulation reproducing experimental results 
	with labelled transitions (see Section 
	\ref{sec:analysis} for notation). 
	\textbf{(c)} Slices of (a) and (b) at various 
	currents: 0.365 mA (feature III), 0.411 mA 
	(sweet spot), 0.333 mA (feature I); 
	experiment is gray, simulation is black. 
	Spectral lines where only one SAA is excited 
	are highlighted with the corresponding colour 
	from \autoref{fig:experiment}. Rabi 
	frequencies $\Omega_{1,2}$ may be extracted 
	as FWHM of the spectral lines 10 and 01, 
	respectively. \textbf{(d)} Simulated 
	population of the state $\ket{10}$ ($\lg 
	P_{\ket{10}}$ is shown with colour). Lines 
	show various transition frequencies from the 
	unperturbed Hamiltonian. Legend labels 
	transitions near the sweet spot current; if 
	elsewhere any two lines form an avoided 
	crossing, the labels should be swapped after 
	the intersection.}
	\label{fig:two-tone}
\end{figure*}

@@

	\includegraphics[width=.7\linewidth]{powerscan_1d}
	\caption{Power dependence of feature II: 
	experiment, simulation and theory. Dashed are 
	the model curves turning to dotted when the 
	model is not expected to be valid (see 
	Sections \ref{sec:theory} and 
	\ref{sec:münchhausen}); model values for 
	$\Omega_{1,2}$ are the same for both (a) and 
	(b): $\Omega_{1,2}/2\pi=$ 4.5, 11.25, 22.5 
	and 45 MHz. \textbf{(a)} Experiment (second 
	cooldown; the parameters are different to 
	those in \autoref{fig:experiment}). The power 
	of the microwave source is increased from -20 
	to 0 dBm, and the corresponding growth of the 
	splitting and the widths of the spectral 
	lines is observed. \textbf{(b)} Simulation 
	with amplitudes of the driving $\Omega_{1,2}$ 
	equal to the model values; other parameters 
	as in \autoref{fig:two-tone}. Note that now 
	colours show the population of the ground 
	state. \textbf{(c)} Linear dependence of the 
	splitting size on the driving voltage of the 
	microwave source $V_{rms} = 
	\sqrt{10^{P_{exc}/10}\cdot 1 \text{ mW} \cdot 
	50\ \Omega}$, ${\Omega_2}/{V_{rms}} = 0.23\ 
	{\text{MHz}}/{\text{mV}}$. From Section 
	\ref{sec:theory}, the splitting size is 
	$\frac{2\sqrt{3}}{3} \Omega_2$.}
	\label{fig:zoom}
\end{figure*}

\begin{figure*}
	\centering
	\includegraphics[width=\linewidth]{topological_splittings}
	\caption{Simulated population of the ground 
	state when the transmons are driven at the 
	same frequency but at different amplitudes 
	$\Omega_{1,2}$. In the top row (middle row), 
	$\Omega_{1(2)}$ is increased while 
	$\Omega_{2(1)} = \text{const} \ll 
	\Omega_{1(2)}$; two topologically different 
	types of anticrossings arise depending on 
	which transmon is driven stronger. In the 
	bottom row, we show how the splittings vanish 
	when the weaker driving is increased to match 
	with the stronger one. Gray dashed lines show 
	the solution with no driving, in black are 
	the model curves based on Sections 
	\ref{sec:theory} and \ref{sec:münchhausen}.}
	\label{fig:difdrive}
\end{figure*}

@@

Having settled the naming system, we continue to 
analyse the plots. Due to the strong driving, we 
observe several multiphoton transitions besides 
the main lines at $\omega_{(1,2)}(I)/2\pi$ (or 
$01$ and $10$ lines). The ${02/2}$ and ${20/2}$ 
are very commonly found for transmons and lie 
$|\alpha_{(1,2)}|/2$ lower than the main lines 
$\omega_{(1,2)}(I	)$. Another two-photon process 
appears as $11/2$ line when two SAAs are excited 
simultaneously. This process is used, for 
example, for doing the bSWAP 
gate\cite{poletto2012entanglement}; in our case, 
it is taking part in formation of feature I. A 
three-photon process $12/3$ is also clearly 
visible just below the $02/2$ line. As we will 
see, it is involved in forming features II and 
III. Notably, transitions $11/2$, ${21/3}$ and 
${12/3}$ are forbidden when there is no 
interaction between transmons ($J=0$). Therefore, 
it is expected that all Roman-numbered features 
should only appear with non-vanishing $\hat 
H_{int}$.

When two lines intersect, they may form an 
avoided crossing if the corresponding matrix 
element of $\hat H_{int}$ is non-zero. In such 
cases, the SAM becomes inseparable with some of 
the eigenstates becoming superpositions of the 
factorized states. For a two-transmon SAM, such 
points are, for instance, crossings between 
${01}$, ${10}$ or $ {11} $, $ {02} $($ {20} $). 
Additionally, marked as feature 3 in 
\autoref{fig:two-tone}, we see an avoided 
crossing between ${12}/3,\ {21}/3$ at the same 
$\Phi_e$ where ${01}$, ${10}$ intersect.

\paragraph{Features I, II and III.} First, we have focused on the feature III and have reproduced this avoided crossing in an additional numerical simulation taking only 2 levels for the transmon 1 and three levels for the transmon 2. Upon this, it has become clear that feature II and feature III actually are of the same nature and differ only by the ordering of the transmons: for II, they appear whence the transition ${01}$ intersects with the two-photon one ${20/2}$ (${10}$ intersects ${02/2}$ in III); one can see this clearly in \autoref{fig:two-tone}~(b).

From \autoref{fig:two-tone}~(d) we conclude that 
avoided crossing in III is between two 
transitions: ${12/3}$ and ${10} - {02}$ 
($\ket{10}\rightarrow\ket{02}$) which are of the 
same frequency when $\omega_1 = 
\omega_2+\alpha_2/2$. The latter process is 
discernible in \autoref{fig:two-tone}~(d) as it 
depopulates ${10}$, but is not visible in 
\autoref{fig:two-tone}~(a),(b). In II, the 
reversed is true: ${21/3}$ and ${01} - {20}$ are 
crossing when $\omega_2 = \omega_1+\alpha_1/2$. 
From additional measurements and simulations, we 
find that the splitting depends on the driving 
power; the experimental and simulated results for 
II are shown in \autoref{fig:zoom}~(a), (b). As 
one can see, the growth of the splitting with 
increasing power is linear: it is roughly equal 
to the FWHM of the ${01}$ spectral line. To fully 
quantify the shape of this splitting, in Section 
\ref{sec:theory} we derive analytical expressions 
for the dashed curves fitting the spectral lines 
in \autoref{fig:zoom}. By measuring the 
dependence of the splitting size on the microwave 
power we confirm its proportionality to the 
signal amplitude (see \autoref{fig:zoom}~(c)).

We see a similar behaviour for feature I: 
increasing drive amplitude on one of the 
transmons while keeping the other one small and 
constant again elicits avoided crossings with the 
proportional size. In \autoref{fig:difdrive} we 
show only the simulation results; an experiment 
is not possible with our sample because there is 
no way to adjust the driving amplitudes 
$\Omega_{1,2}$ individually. We note that two 
qualitatively different patterns arise depending 
on which of the transmons is driven stronger than 
the other. From this and from the shape of the 
splitting in feature I of 
\autoref{fig:two-tone}~(a), we can infer that 
$\Omega_1/\Omega_2 \approx 2$ there (also 
consistent with the 01, 10 linewidths in 
\autoref{fig:two-tone}~(c)).

These observations mean that effects I -- III are 
caused by light dressing. In the case III, the 
first transmon is dressed by a strong resonant 
field; in case II, the second one; finally, in 
case I, both transmons are dressed at the same 
time. We will discuss these effects in greater 
detail in Section \ref{sec:theory}.

@@

Feature 4 is also explained by the unperturbed 
model and is caused by several spectral lines and 
a pair of avoided crossings near a single point 
(dotted lines in \autoref{fig:two-tone}~(d)). It 
appears at the point where ${02/2}$ intersects 
${20/2}$ and is just barely visible in the 
experimental data because of the noise. Feature 5 
is located at the intersection between ${20/2}$ 
and normally invisible ${10} - {02}$, and can be 
found in the experimental data, too.

Finally, when the coupling is turned off ($J=0$) in the simulation, the system does not demonstrate any of the described details. This means that all these effects can only be attributed to the SAM as a whole.

@@

Since we had already connected the additional 
avoided crossings with the light dressing, it was 
natural to expect an Autler-Townes-like effect to 
be at the root of the additional spectral lines. 
For a three-level system, the standard A-T effect 
is reviewed in Appendix \ref{sec:3-level-at}. 
However, in our case the level structure and the 
effect itself are more complicated.

First of all, since during the spectroscopy we 
apply only a single microwave tone ($\omega_d^1 = 
\omega_d^2$), for the A-T effect it has to be 
simultaneously the coupler and the probe; the 
latter must be much weaker than the former, as 
well. These conditions are satisfied when 
$\omega_{\{2,1\}} = 
\omega_{\{1,2\}}+\alpha_{\{1,2\}}/2$  where we 
can simultaneously excite transitions $01 (10)$ 
and $20/2 (02/2)$ (features II and III, 
respectively). Since the two-photon Rabi 
frequency is much smaller than the single-photon 
$\Omega_2$, it is natural to view this two-photon 
excitation as the probing process which does not 
affect the level structure. In contrast, 
single-photon excitation is strong enough to 
dress the system. In other words, in our case the 
A-T coupling operator is $\hat H_{d}^1$ (strong), 
and the probing operator is $\hat H_{d}^2$ (weak 
in the two-photon regime). However, their 
separation in our case is not in frequency, but 
in the Hilbert subspaces they act upon.

Similarly, for feature I, the simultaneously 
excited transitions are $01(10)$ and the 
two-photon $11/2$. However, as we demonstrate in 
\autoref{fig:difdrive}, for the avoided crossings 
in I to be clearly observed it is required that 
$\Omega_{\{1,2\}} \gg \Omega_{\{2,1\}}$.

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{main_scheme_2}  
	\caption{Explaining feature III. \textbf{(a)} 
	Schematic of the transition frequencies near 
	III (not to scale). Red dashed line shows the 
	current (0.36 mA) where the first transmon 
	(orange) is below the second one (blue) 
	exactly by $\alpha_2/2$ and several 
	transitions become resonant. So far we assume 
	that each transmon is driven at its own 
	frequency. \textbf{(b)} System level 
	structure at the resonant point including the 
	driving $\hat H_{d}^1$ of the first transmon 
	by a strong signal of amplitude $\Omega_1$ 
	(orange ellipses) at a small detuning 
	$\Delta_1$ from $\omega_1$. The second 
	transmon driving is not shown here. Action of 
	$\hat H_{int}$ in RWA is depicted as 
	orange-blue circles. \textbf{(c)} In the 
	frame rotating with the drive of the first 
	transmon, all the states $\ket{0j},\ket{1j}$ 
	become nearly degenerate ($\omega_1 
	\rightarrow \Delta_1$). Dressing by the 
	strong excitation increases this splitting to 
	$\Omega_1^R = \sqrt{\Omega_1^2 + 
	\Delta_1^2}$. \textbf{(d)} Transitions in the 
	light-dressed system when the second transmon 
	is excited (level subspaces coupled by $\hat 
	H_{d}^2$ are shown with blue ellipses). In 
	the left part of the panel, all possible 
	two-photon transitions near $\omega_1$ are 
	depicted: the green transitions are not 
	shifted in frequency, the red are red-shifted 
	by $\Omega^R_1/2$ and the blue are 
	blue-shifted by $\Omega^R_1/2$. In the right 
	part, the most contributing trajectories are 
	depicted; red crosses show transitions that 
	are forbidden without the coupling $J$.}
	\label{fig:main_scheme}
\end{figure}

@@

In \autoref{fig:main_scheme}, we elaborate on how 
exactly the A-T effect occurs for feature III. 
For simplicity, we will temporarily assume that 
each transmon is driven at its own frequency 
(this assumption will be lifted in the following 
section). For convenience, in 
\autoref{fig:main_scheme}~(a) we schematically 
reproduce the transitions near III where the 
first transmon (orange) is below the second 
(blue), and the resonance point in current is 
shown with a dashed red line. Next, 
\autoref{fig:main_scheme}~(b) demonstrates the 
level structure of the SAM at 0.36 mA. Detuned by 
$\Delta_1$ from $10$, single-photon driving of 
$\hat H_d^1$ is shown with orange ellipses while 
much weaker two-photon $\hat H_d^2$ is not shown 
yet. Since from numerical simulations we know 
that the third level of the first transmon is not 
necessary to observe the splitting, $\ket{20}$ is 
shown transparent, and states $\ket{21},\ 
\ket{22}$ are not shown.

@@

Finally, in \autoref{fig:main_scheme}~(d) we demonstrate possible two-photon transitions between the resulting eigenstates due to $\hat H_{d}^2$. In the left part of the panel, the unmodified transition at $\omega_1$ and two sidebands at $\omega_1 \pm \Omega_1^R/2$. The right part describes the mechanism of these two-photon processes through virtual excitations of the intermediate states. From here it becomes obvious that without the transmon-transmon interaction the sideband transitions are forbidden due the selection rule: $\bra{a,j}\hat{\mathbbm{1}}\otimes \hat n_2 \ket{b, j+1} = 0$ since $\braket{a}{b} = 0$. However, we will show that they become allowed in the second order in $J$ when the coupling is turned on.  Remarkably, due to the two-photon nature of the transitions, the Autler-Townes splitting in this case will be just $\Omega_1^R$.

Now, we will repeat this reasoning using a 
quantitative mathematical model. We start from 
the initial Hamiltonian \autoref{Hsystem}. To 
move to the rotating frame with 
\autoref{eq:rotation} and apply the RWA, will use 
the following operator:
\begin{equation}
R = \exp[-it \omega_d^1 
(b^{\dagger}b+c^{\dagger}c)].
\end{equation}  
Note that we rotate both transmon subspaces simultaneously in contrast to what is shown in \autoref{fig:main_scheme} because below it will be convenient to have time-independent $\hat H_{int}$. Now,
\begin{equation}
\begin{aligned}
\omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_{(1,2)} - \omega_d^{1},\\
\hat H_{int} &\rightarrow  \hbar J \left[\hat \sigma_+ \hat c + \hat \sigma_-\hat c^\dag \right],\\
\hat H_{d}^1 &\rightarrow \frac{\hbar \Omega_1}{2} \hat \sigma_x,\ 
\hat H_{d}^2 \rightarrow \frac{\hbar \Omega_2}{2}(\hat c e^{i\delta t}  + \hat c^\dag e^{-i\delta t}),
\end{aligned}
\end{equation}
where $\delta = \omega_{d}^2 - \omega_{d}^1$.

@@

The time-dependent perturbation theory that we use to calculate the transition rates of the two-photon processes stimulated by $\hat V_t$ is reviewed in Appendix \ref{sec:2pp}. Using the corrected eigenstates $\ket{k}$ and neglecting small terms we obtain the following expression for the transition rates per unit time\cite{faisal2013theory}:
\begin{equation}
\begin{aligned}
R^{(2)}_{1\rightarrow 6} &\approx 2\pi\Omega_2^4 
\frac{18 J^4 \left(2 \alpha + 
\text{$\Omega_1$}\right)^2}{\alpha 
^{6}\Omega_1^2},\\
R^{(2)}_{2\rightarrow 5} &\approx 2\pi\Omega_2^4 
\frac{18 J^4 \left(2 \alpha - \text{$\Omega_1
		$}\right)^2}{\alpha ^{6}\Omega_1^2},
\end{aligned}\label{eq:rates}
\end{equation}
when $\alpha \gg \Omega_1, \Omega_2, J$ which is 
true for our setup. From \autoref{eq:rates} 
follows that the sideband transitions are 
prohibited without the interaction in the SAM 
$(J=0)$, and the extra avoided crossings will not 
be observed.

@@

As one can see from \autoref{fig:difdrive}, only the two-photon transition $11/2$ is affected and experiences a frequency shift approaching the 01-10 intersection while the other spectral lines are not moving. Similarly to II and III, in the frame rotating with the second transmon it tuns into two different single-photon transitions for $\hat H_d^1$ located at $\omega_1 \pm \Omega_2^R$, see \autoref{fig:featureI}~(b). We will show below that in the experiment with a single excitation frequency, it is not possible to observe both transitions simultaneously; this is clearly visible in \autoref{fig:difdrive}. Instead, we observe one line to the left and the other to the right from the $01-10$ intersection.

@@

\autoref{eq:topo_comm} is used to plot the black 
dashed curves in \autoref{fig:difdrive} taking 
the $\Omega_{1,2}$ values from the simulation 
parameters shown therein. The frequencies 
$\omega_{1,2}$ are extracted from the fits to the 
visible spectral lines. We find good agreement 
between the model and the simulated data.

>>>>

	\includegraphics[width=.495\linewidth]{main_picture_slices}
	\includegraphics[width=.495\linewidth]{stationary}
	\caption{Two-tone spectroscopy: experiment 
	and numerical modelling. \textbf{(a)} 
	Experimental data. Colour shows the real part 
	of complex transmission  through the sample. 
	Two transmons are aligned as in 
	\autoref{fig:experiment}~(c) and form a 
	symmetric picture. Experimental data contain 
	an additional horizontal line from a 
	parasitic resonance interacting with the 
	readout resonator. Three avoided crossings 
	not predicted by the unperturbed model are 
	shown in insets I, II and III; other 
	pronounced features reproduced by the 
	modelling are shown with Arabic markers (see 
	text for description). \textbf{(b)} Numerical 
	simulation reproducing experimental results 
	with labelled transitions (see Section 
	\ref{sec:analysis} for notation). 
	\textbf{(c)} Slices of (a) and (b) at various 
	currents: 0.365 mA (feature III), 0.411 mA 
	(sweet spot), 0.333 mA (feature I); 
	experiment is gray, simulation is black. 
	Spectral lines where only one SAA is excited 
	are highlighted with the corresponding colour 
	from \autoref{fig:experiment}. Rabi 
	frequencies $\Omega_{1,2}$ may be extracted 
	as FWHM of the spectral lines 10 and 01, 
	respectively. \textbf{(d)} Simulated 
	population of the state $\ket{10}$ ($\lg 
	P_{\ket{10}}$ is shown with colour). Lines 
	show various transition frequencies from the 
	unperturbed Hamiltonian. In the legend, the 
	transitions are labelled near the sweet spot current; if 
	elsewhere any two lines form an avoided 
	crossing, the labels should be swapped after 
	the intersection.}
	\label{fig:two-tone}
\end{figure*}

@@

	\includegraphics[width=.7\linewidth]{powerscan_1d}
	\caption{Power dependence of feature II: 
	experiment, simulation and analytic model. Dashed are the model curves turning to dotted when the 
	model is not expected to be valid (see 
	Sections \ref{sec:theory} and 
	\ref{sec:münchhausen}); model values for 
	$\Omega_{1,2}$ are the same for both (a) and 
	(b): $\Omega_{1,2}/2\pi=$ 4.5, 11.25, 22.5 
	and 45 MHz. \textbf{(a)} Experiment (second 
	cooldown; the parameters are different to 
	those in \autoref{fig:experiment}). The power 
	of the microwave source is increased from -20 
	to 0 dBm, and the corresponding growth of the 
	splitting and the widths of the spectral 
	lines is observed. \textbf{(b)} Simulation 
	with amplitudes of the driving $\Omega_{1,2}$ 
	equal to the model values; other parameters 
	as in \autoref{fig:two-tone}. Note that now 
	colours show the population of the ground 
	state. \textbf{(c)} Linear dependence of the 
	splitting size on the driving voltage of the 
	microwave source $V_{rms} = 
	\sqrt{10^{P_{exc}/10}\cdot 1 \text{ mW} \cdot 
	50\ \Omega}$, ${\Omega_2}/{V_{rms}} = 0.23\ 
	{\text{MHz}}/{\text{mV}}$. From Section 
	\ref{sec:theory}, the splitting size is 
	$\frac{2\sqrt{3}}{3} \Omega_2$.}
	\label{fig:zoom}
\end{figure*}

\begin{figure*}
	\centering
	\includegraphics[width=\linewidth]{topological_splittings}
	\caption{Simulated population of the ground 
	state when the transmons are driven at the 
	same frequency but at different amplitudes 
	$\Omega_{1,2}$. In the top row (middle row), 
	$\Omega_{1(2)}$ is increased while 
	$\Omega_{2(1)} = \text{const} \ll 
	\Omega_{1(2)}$; two topologically different 
	types of anticrossings arise depending on 
	which transmon is driven stronger. In the 
	bottom row, we show how the splittings vanish 
	when the weaker driving is increased to match 
	with the stronger one. Gray dashed lines show 
	the solution without driving, in black are 
	the model curves based on Sections 
	\ref{sec:theory} and \ref{sec:münchhausen}.}
	\label{fig:difdrive}
\end{figure*}

@@

Having settled the naming system, we continue to 
analyse the plots. Due to the strong driving, we 
observe several multiphoton transitions besides 
the main lines at $\omega_{(1,2)}(I)/2\pi$ (or 
$01$ and $10$ lines). The ${02/2}$ and ${20/2}$ 
are very commonly found for transmons and lie 
$|\alpha_{(1,2)}|/2$ lower than the main lines 
$\omega_{(1,2)}(I)$. Another two-photon process 
appears as $11/2$ line when two SAAs are excited 
simultaneously. This process is used, for 
example, for doing the bSWAP 
gate\cite{poletto2012entanglement}; in our case, 
it is taking part in formation of feature I. A 
three-photon process $12/3$ is also clearly 
visible just below the $02/2$ line. As we will 
see, it is involved in forming features II and 
III. Notably, transitions $11/2$, ${21/3}$ and 
${12/3}$ are forbidden when there is no 
interaction between transmons ($J=0$). Therefore, 
it is expected that all Roman-numbered features 
should only appear with non-vanishing $\hat 
H_{int}$.

When two lines intersect, they may form an 
avoided crossing even for an unperturbed model if 
the corresponding matrix 
element of $\hat H_{int}$ is non-zero. In such 
cases, the SAM becomes inseparable with some of 
the eigenstates becoming superpositions of the 
factorized states. For a two-transmon SAM, such 
points are, for instance, anticrossings between 
${01}$,${10}$ or $ {11} $,$ {02} $($ {20} $) 
visible clearly in \autoref{fig:two-tone}~(d). 
Additionally, marked as feature 3 in 
\autoref{fig:two-tone}, we see an avoided 
crossing between ${12}/3,\ {21}/3$ at the same 
current where ${01}$, ${10}$ intersect.

\paragraph{Analysing features I, II and III.} 
First, we have reproduced the avoided crossing of feature III in an additional numerical simulation taking only 2 levels for the transmon 1 and three levels for 
the transmon 2. Upon this, it has become clear 
that features II and III are actually of 
the same nature and differ only by the ordering 
of the transmons: for II, they appear whence the 
transition ${01}$ intersects with the two-photon 
one ${20/2}$, and for III when ${10}$ intersects ${02/2}$; 
one can see this clearly in 
\autoref{fig:two-tone}~(b).

From \autoref{fig:two-tone}~(d) we conclude that 
avoided crossing in III is between two 
transitions: ${12/3}$ and ${10} - {02}$ 
($\ket{10}\rightarrow\ket{02}$) which are of the 
same frequency when $\omega_1 = 
\omega_2+\alpha_2/2$. The latter process depopulating $01$ is better discernible in \autoref{fig:two-tone}~(d) 
than in \autoref{fig:two-tone}~(a), (b). For II, the 
opposite is true: ${21/3}$ and ${01} - {20}$ are 
crossing when $\omega_2 = \omega_1+\alpha_1/2$. 
From additional measurements and simulations, we 
find that the splitting depends on the driving 
power; the experimental and simulated results for 
II are shown in colour in \autoref{fig:zoom}~(a), (b), respectively. As one can see, the growth of the splitting with 
increasing power is linear: it is roughly equal 
to the FWHM of the ${01}$ spectral line. To fully 
quantify the shape of this splitting, in Section 
\ref{sec:theory} we derive analytical expressions 
for the dashed curves fitting the spectral lines 
in \autoref{fig:zoom}. In \autoref{fig:zoom}~(c), blue points, we present splitting sizes extracted by fitting of the model to the data as in \autoref{fig:zoom}~(a) for various power values of the microwave generator connected to the excitation waveguide. As one can see from the linear approximation of the points, the splitting indeed is simply proportional to the RMS voltage of the signal. From the model, we expect that the minimal distance between curves in the anticrossing is equal to $\frac{2\sqrt{3}}{3} \Omega_2$; using this relation, we extract the proportionality coefficient between $\Omega_2$ and $V_{rms}$ is around $0.23$ MHz/mV from the linear fit.

In \autoref{fig:difdrive}, we demonstrate a similar power dependence of feature I: increasing drive amplitude on one of the 
transmons while keeping the other one small and 
constant again elicits avoided crossings with the 
proportional size. We  show only the simulation results; an experiment is not possible with our sample because, since we have just a single excitation line, there is 
no way for us to control the driving amplitudes 
$\Omega_{1,2}$ individually. We note that two 
qualitatively different patterns arise depending 
on which of the transmons is driven stronger than 
the other. From this and from the shape of the 
splitting in feature I of 
\autoref{fig:two-tone}~(a), we can infer that 
$\Omega_1/\Omega_2 \approx 2$ there (also 
consistent with the 01, 10 linewidths in 
\autoref{fig:two-tone}~(c)). If in contrast both transmons are driven with equal amplitudes, the avoided crossing vanishes. As can be seen from black dashed lines in \autoref{fig:difdrive}, all these cases are explained well by our analytical model described in detail in Sections \ref{sec:theory} and \ref{sec:münchhausen}}.

From all presented observations, we conclude that effects I -- III 
are caused by light dressing. In the case III, the 
first transmon is dressed by a strong resonant 
field; in case II, the second one; finally, in 
case I, both transmons may be dressed at the same 
time. We will discuss these effects in greater 
detail in Sections \ref{sec:theory} and \ref{sec:münchhausen}.

@@

Feature 4 is also explained by the unperturbed 
model and is caused by several spectral lines and 
a pair of avoided crossings near a single point 
(dotted lines in \autoref{fig:two-tone}~(d)). It 
appears at the point where ${02/2}$ intersects 
${20/2}$ and is just barely visible in the 
experimental data because of the noise.

Feature 5 is located at the intersection between ${20/2}$ 
and ${10} - {02}$, and can be 
found in the experimental data, too.

In conclusion to this section, we note that when the coupling is turned off ($J=0$) in the simulation, the system does not demonstrate any of the described details. This means that all these effects can only be attributed to the SAM as a whole.

@@

Since we had already connected the additional 
avoided crossings with the light dressing, it was 
natural to expect an Autler-Townes-like effect to 
be at the root of the additional spectral lines. 
For a three-level system, the standard A-T effect 
is revised in Appendix \ref{sec:3-level-at}. 
However, in our case the level structure and the 
effect itself are more complicated.

First of all, since during the spectroscopy we 
apply only a single microwave tone ($\omega_d^1 = 
\omega_d^2$), it has to be 
simultaneously the coupler and the probe
in terms of the standard A-T effect; moreover, the 
probe must be much weaker than the coupler. 
Fortunately, all these conditions are satisfied near feature II(III) when 
$\omega_{\{2,1\}} = 
\omega_{\{1,2\}}+\alpha_{\{1,2\}}/2$  where we 
can simultaneously excite transitions $01 (10)$ 
and $20/2 (02/2)$. Since the two-photon Rabi 
frequency is much smaller than the single-photon 
$\Omega_2$, it is natural to view this two-photon 
excitation as the probing process which does not 
affect the level structure. In contrast, 
single-photon excitation is strong enough to 
dress the system. In other words, in our case the 
A-T coupling operator is $\hat H_{d}^1$ (strong), 
and the probing operator is $\hat H_{d}^2$ (weak 
in the two-photon regime). However, their 
separation in our case is not in frequency, but 
in the Hilbert subspaces they act upon and in the number of participating photons.

For feature I, the simultaneously 
excited transitions are $01,\ 10$ and the 
two-photon $11/2$. In this case, the weak two-photon process is probing transitions in the doubly-dressed SAM. We find that if SAAs are dressed equally, $11/2$ does not form an avoided crossing, and for it to be clearly observed it is required that 
$\Omega_{\{1,2\}} \gg \Omega_{\{2,1\}}$.

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{main_scheme_2}  
	\caption{Explaining feature III. \textbf{(a)} 
	Schematic of the transition frequencies near 
	III (not to scale). Red dashed line shows the 
	current (0.36 mA) where the first transmon 
	(orange) is below the second one (blue) 
	exactly by $\alpha_2/2$ and several 
	transitions become resonant. Here we assume 
	that each transmon is driven at its own 
	frequency. \textbf{(b)} System level 
	structure at the resonant point and the first transmon 
	driving of amplitude $\Omega_1$ 
	(orange ellipses) at a small detuning 
	$\Delta_1$ from $\omega_1$. The second 
	transmon driving is not shown here. Action of 
	$\hat H_{int}$ in RWA is depicted as 
	orange-blue circles. \textbf{(c)} In the 
	frame rotating with $\hat 
	H_{d}^1$, states $\ket{0j},\ket{1j}$ 
	become nearly degenerate ($\omega_1 
	\rightarrow \Delta_1$). Dressing increases this splitting to 
	$\Omega_1^R = \sqrt{\Omega_1^2 + 
	\Delta_1^2}$. \textbf{(d)} Transitions in the 
	dressed system induced by $\hat 
	H_{d}^2$ (coupled level subspaces are shown with blue ellipses). In 
	the left part of the panel, all possible 
	two-photon transitions near $\omega_1$ are 
	depicted: the blue transitions are not 
	shifted in frequency, the light blue ones are shifted 
	by $\pm\Omega^R_1/2$. In the right 
	part, the most contributing trajectories are 
	depicted; gray crosses show transitions that 
	are forbidden without the coupling $J$.}
	\label{fig:main_scheme}
\end{figure}

@@

In \autoref{fig:main_scheme}, we elaborate on which transitions
are involved in the A-T-like effect for feature III. 
For simplicity, we will temporarily assume that 
each transmon is driven at its own frequency 
(this assumption will be lifted in the following 
section). For convenience, in 
\autoref{fig:main_scheme}~(a) we schematically 
reproduce the transitions near III where the 
first transmon (orange) is below the second 
(blue), and the resonance point in current is 
shown with a dashed red line. Next, 
\autoref{fig:main_scheme}~(b) demonstrates the 
level structure of the SAM at 0.36 mA. Detuned by 
$\Delta_1$ from $10$, single-photon driving of 
$\hat H_d^1$ is shown with orange ellipses while 
much weaker two-photon $\hat H_d^2$ is not shown 
yet. Since from numerical simulations we know 
that the third level of the first transmon is not 
necessary to observe the splitting, $\ket{20}$ is 
shown transparent, and states $\ket{21},\ 
\ket{22}$ are not shown.

@@

Finally, in \autoref{fig:main_scheme}~(d) we demonstrate possible two-photon transitions between the dressed states induced by the second transmon driving $\hat H_{d}^2$. In the left part of the panel, one can find the unmodified two-photon transition $02/2$ at $\omega_1$ and two sidebands at $\omega_1 \pm \Omega_1^R/2$. This picture finally explains the observed triplet transition of feature III. The right part describes the mechanism of these two-photon processes through virtual excitations of the intermediate states. From here it becomes obvious that without the transmon-transmon interaction the sideband transitions are forbidden due the selection rule: $\bra{a,j}\hat{\mathbbm{1}}\otimes \hat n_2 \ket{b, j+1} = 0$ since $\braket{a}{b} = 0$. However, we will show that they become allowed in the second order in $J$ when the coupling is turned on.

Now, we will repeat this reasoning using a 
quantitative mathematical model. We start from 
the initial Hamiltonian \autoref{Hsystem}. To 
move to the rotating frame with 
\autoref{eq:rotation} and apply the RWA, we use 
the following operator:
\begin{equation}
R = \exp[-it \omega_d^1 
(b^{\dagger}b+c^{\dagger}c)].
\end{equation}  
Note that now we rotate both transmon subspaces simultaneously in contrast to what is shown in \autoref{fig:main_scheme} because below it will be convenient to have time-independent $\hat H_{int}$. Now,
\begin{equation}
\begin{aligned}
\omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_{(1,2)} - \omega_d^{1},\\
\hat H_{int} &\rightarrow  \hbar J \left[\hat \sigma_+ \hat c + \hat \sigma_-\hat c^\dag \right],\\
\hat H_{d}^1 &\rightarrow \frac{\hbar \Omega_1}{2} \hat \sigma_x,\ 
\hat H_{d}^2 \rightarrow \frac{\hbar \Omega_2}{2}(\hat c e^{i\delta t}  + \hat c^\dag e^{-i\delta t}),
\end{aligned}
\end{equation}
where $\delta = \omega_{d}^2 - \omega_{d}^1$.

@@

The time-dependent perturbation theory that we use to calculate the transition rates of the two-photon processes stimulated by $\hat V_t$ is reviewed in Appendix \ref{sec:2pp}. Using the corrected eigenstates $\ket{k}$ and neglecting small terms, we obtain the following expressions for the transition rates per unit time\cite{faisal2013theory}:
\begin{equation}
\begin{aligned}
R^{(2)}_{1\rightarrow 6} &\approx 2\pi\Omega_2^4 
\frac{18 J^4 \left(2 \alpha + 
\text{$\Omega_1$}\right)^2}{\alpha 
^{6}\Omega_1^2},\\
R^{(2)}_{2\rightarrow 5} &\approx 2\pi\Omega_2^4 
\frac{18 J^4 \left(2 \alpha - \text{$\Omega_1
		$}\right)^2}{\alpha ^{6}\Omega_1^2},
\end{aligned}\label{eq:rates}
\end{equation}
when $\alpha \gg \Omega_1, \Omega_2, J$ which is 
true for our setup. From \autoref{eq:rates} 
follows that the sideband transitions are 
prohibited without the interaction in the SAM 
$(J=0)$, and the extra avoided crossings will not 
be observed.

@@

As one can see from \autoref{fig:difdrive}, only the two-photon transition $11/2$ is affected and deviates from unperturbed spectrum when approaching the 01-10 intersection while the other spectral lines are not moving. Similarly to II and III, in the frame rotating with the second transmon it tuns into two different single-photon transitions for $\hat H_d^1$ located at $\omega_1 \pm \Omega_2^R$, see \autoref{fig:featureI}~(b). We will show below that in the experiment with a single excitation frequency, it is not possible to observe both transitions simultaneously; this is clearly visible in \autoref{fig:difdrive}. Instead, we observe one line to the left and the other to the right from the 01-10 intersection.

@@

\autoref{eq:topo_comm} is used to plot the black 
dashed curves in \autoref{fig:difdrive} taking 
the $\Omega_{1,2}$ values from the simulation 
parameters shown therein. The frequencies 
$\omega_{1,2}$ are extracted from the fits to the 
visible spectral lines. We again find good agreement 
between the model and the simulated data.
